Differential Expression - MSSM-Penn-Pitt - ACC - Dx_Sex

### 2020-07-29 individual-cohorts/MSSM-Penn-Pitt_ACC_DE.Rmd
residuals bug fixed
fix plot scale

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## Load required libraries
library(data.table)
library(dplyr)
library(R.utils)
library(psych)
library(lme4)
library(variancePartition)
library(synapser)
library(knitr)
library(githubr)
library(CovariateAnalysis)
library(edgeR)
library(WGCNA)

@@

RESIDUAL.GENE_EXPRESSION = stats::residuals(ADJUSTED.FIT, CQN.GENE_EXPRESSION)
```

@@

### Differential expression analysis (SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
adjust.covars <- adjust.covars[!(adjust.covars %in% "RIN2")]
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))    
```
#drop redundancy - RIN2 or RIN
#use canCorPairs() to test colinearity, don't want var of interest to be correlated
#leave out random effects
`r formula`

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1))
p = p + scale_color_manual(values = c('green','grey','red')) + theme_bw() %+replace% theme(legend.position = 'top')
p = p + facet_grid(.~Comparison, scales = 'fixed')
p
```

>>>>

```{r libs, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
## Load required libraries
library(data.table)
library(dplyr)
library(R.utils)
library(psych)
library(lme4)
library(variancePartition)
library(synapser)
library(knitr)
library(githubr)
library(CovariateAnalysis)
library(edgeR)
library(WGCNA)
library(biomaRt)

@@

RESIDUAL.GENE_EXPRESSION = residuals(ADJUSTED.FIT, CQN.GENE_EXPRESSION)
```

@@

### Differential expression analysis (SCZ - Control - Other)
Genes that are differentially expressed at an FDR <= 0.05 are:
```{r set-formula}
adjust.covars <- adjust.covars[!(adjust.covars %in% "RIN2")]
formula <- glue::glue("~ 0 + ", glue::glue_collapse(adjust.covars, sep = " + "), " + ", glue::glue_collapse(glue::glue("(1|{random_effect})"), sep = " + "))    
```

`r formula`

@@

p = ggplot(DE, aes(y = -log10(adj.P.Val), x = logFC, color = Direction)) + geom_point() + xlim(c(-1,1)) + ylim(c(0,100))
p = p + scale_color_manual(values = c('green','grey','red')) + theme_bw() %+replace% theme(legend.position = 'top')
p = p + facet_grid(.~Comparison, scales = 'fixed')
p
```
